The analogy of the cohort-equations paradigm to the compartmental epidemic models

### 2021-05-26 cohort.tex
Meeting with Ali
still working
adding SIR with testing example

\documentclass[12pt]{article}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{grffile}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage[nameinlink,capitalize]{cleveref}
\usepackage{cleveref}
\usepackage[margin=1in]{geometry}
\usepackage{lineno}\renewcommand\thelinenumber{\color{gray}\arabic{linenumber}}
\usepackage{pdflscape}
\usepackage{enumerate}

\newcommand{\todo}[1]{\comment{red}{TODO}{#1}}

\usepackage{xspace}

@@

\item 
Finding the intrinsic infectiousness kernel by integrating the cohort Eq. and solving for its time evolution, thus
the solution would be 
\begin{equation}
\label{eq:I}
\vec I(\tau) = \exp(-V\tau) \vec I(0).
\end{equation}
The kernel will be 
\begin{equation}
\label{eq:kernel}
\vec K(\tau) = F \vec I(\tau), 
\end{equation}
where $F$ is the matrix of new infections in the compartment framework.
Note that the n-by-n matrix $\exp(-V\tau)$ is the probability of being infected and stay infectious at time $\tau$. 
% where $\exp(-V\tau)=\sum_{n=0}^\infty \tau^n (-V)^n/n!$.

\item
Calculating $\vec R$ by integrating kernel $\vec K(\tau)$. Note that $\R$ would be the non-negative element of $\vec R$.
\end{enumerate}
Note that in the compartment framework \citep{van2002reproduction}, steps 2 and 3 are combined.
%%%%%%%%%%%%%%%%%%%%
\section{Examples}

@@

%%%%%%%%%%%%%%%%%%%%

>>>>

\documentclass[12pt]{article}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{grffile}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage[nameinlink,capitalize]{cleveref}
\usepackage{cleveref}
\usepackage[margin=1in]{geometry}
\usepackage{lineno}\renewcommand\thelinenumber{\color{gray}\arabic{linenumber}}
\usepackage{pdflscape}
\usepackage{enumerate}
\usepackage{xspace}

\newcommand{\ali}[1]{\comment{magenta}{Ali}{#1}}
\newcommand{\jd}[1]{\comment{blue}{JD}{#1}}
\newcommand{\david}[1]{\comment{red}{DJDE}{#1}}
\newcommand{\bmb}[1]{\comment{red}{BMB}{#1}}
\newcommand{\todo}[1]{\comment{red}{TODO}{#1}}

\newcommand*\subtxt[1]{_{\textnormal{#1}}}
\DeclareRobustCommand\_{\ifmmode\expandafter\subtxt\else\textunderscore\fi}

@@

\item 
Finding the intrinsic infectiousness kernel by integrating the cohort Eq. and solving for its time evolution, thus
the solution would be 
\begin{equation}
\label{eq:I}
\vec I(\tau) = \exp(-V\tau) \vec I(0).
\end{equation}
The kernel will be 
\begin{equation}
\label{eq:kernel}
\vec K(\tau) = F \vec I(\tau), 
\end{equation}
where $F$ is the matrix of new infections in the compartment framework.
Note that the n-by-n matrix $\exp(-V\tau)$ is the probability of being infected and stay infectious at time $\tau$.

\item
Calculating the next-generation vector $\vec G$ (\ali{feels odd here, help! also check Heesterbeek work what he calls this}) is
\begin{equation}
\label{eq:ng} %next generation
\vec G = \int_0^\infty \vec K(\tau) d\tau.
\end{equation}
Note that $\R$ would be the non-zero element of $\vec G$.
\end{enumerate}
Note that in the compartment framework \citep{van2002reproduction}, steps 2 and 3 are combined.
%%%%%%%%%%%%%%%%%%%%
\section{Examples}

@@

\subsection{SIR with testing and isolation}
The model can be summarized in the form of following matrices.
\begin{align}
\label{FV}
F =&\beta/N_0 \left[ \begin {array}{c} S\_u^* \\ (1-\theta\_w)S\_n^* \\ 0 \\ 0 \end {array} \right]
        \left[ \begin {array}{cccc} 1, \, 1-\theta\_w, \, 1-\theta\_w, \, 1-\theta\_c \end {array} \right], \text{and}\\  V=&
 \left[ \begin {array}{cccc}  
\hat F_I+\gamma&-\omega&0&0\\
-(1-p_I)\hat F_I&\omega+\gamma&0&0\\
-p_I \hat F_I&0&\omega+\gamma&0\\
0&0&-\omega&\gamma
\end {array} \right].
\end{align}

Let the test be perfectly sensative, that is $p_I=1$.

{\it Step 1;} The cohort Eq.~ is
\begin{align}
\vec I'=-V\,\vec I,~~ \text{where}~~ \vec I(\tau)=\left[ \begin {array}{c} I\_u(\tau)\\I_n(\tau)\\I_p(\tau)\\I_c(\tau) \end {array} \right], ~~
\vec I(0)=\left[ \begin {array}{c} S\_u^*\\S\_n^*\\0\\0 \end {array} \right].
\end{align}
Solving for $\vec I(\tau)$ by finding the eigenvalues and eigenvectors of the above linear system results in
\begin{align}
\vec I(\tau)=&
c_1\,\exp(-\gamma\,\tau)\,\left[ \begin {array}{c} 0\\0\\0\\1 \end {array} \right] 
+c_2\,\exp(-(F_I+\gamma)\,\tau)\,\left[ \begin {array}{c} \frac{F_I-\omega}{\omega}\\0\\\frac{-F_I}{\omega}\\1 \end {array} \right]
+c_3\,\exp(-(\omega+\gamma)\,\tau)\,\left[ \begin {array}{c} 0\\0\\-1\\1 \end {array} \right] \\\notag
+& c_4\,\exp(-(\omega+\gamma)\,\tau)\,\Big(\tau\,\left[ \begin {array}{c} 0\\0\\-1\\1 \end {array} \right]+
\left[ \begin {array}{c} \frac{-1}{F_I}\\ \frac{\omega-F_I}{F_I\,\omega}\\ \frac{1}{\omega}\\0 \end {array} \right]\Big),
\end{align}
where 
\begin{align}
c_1=&1\\
c_2=&\frac{\omega}{F_I-\omega}(S\_u^*-\frac{\omega}{F_I-\omega}\,S\_n^*)\\
c_3=&\frac{-F_I}{F_I-\omega}(1-\frac{\omega}{F_I-\omega}S\_n^*)\\
c_4=&\frac{-\omega\,F_I}{F_I-\omega}S\_n^*.
\end{align}

{\it Step 2;} The kernel is
\begin{align}
\vec K(\tau)= F \vec I(\tau)
\end{align}

{\it Step 3;} The next-generation vector is $\vec G$ as follows.
\begin{align}
\vec G=&\int_0^\infty \vec K(\tau) d\tau\\
=&
\end{align}
%%%%%%%%%%%%%%%%%%%%
